Emittance preservation of an electron beam in a loaded quasi-linear plasma wakefield

### 2017-10-12 Tex/Paper.tex
Corrections from Erik

Our base case showed some robustness to a small offset from the proton beam axis on the order of one $\sigma_{x}$, but
with a cost in the fraction of the beam which retains its initial emittance. Figure~\ref{Fig:BeamQOffset} shows the
correlation between this ratio for a range of offsets up to $3.2\cdot\sigma_{x}$. The effect on the head of the beam,
shown in Figs.~\ref{Fig:BeamEmitt} and~\ref{Fig:BeamFilament}, increases with larger offsets causing the section of the
beam being defocused to extend backwards to the point where the witness beam wakefields are no longer in the blow-out
regime. At around $3\cdot\sigma_{x}$ emittance is no longer preserved at all.

>>>>

Our base case showed some robustness to a small offset from the proton beam axis on the order of one $\sigma_{x,eb}$,
but with a reduction of the fraction of the beam which retains its initial emittance. Figure~\ref{Fig:BeamQOffset} shows
the correlation between this ratio for a range of offsets up to $3.2\cdot\sigma_{x,eb}$. The effect on the head of the
beam, shown in Figs.~\ref{Fig:BeamEmitt} and~\ref{Fig:BeamFilament}, increases with larger offsets causing the section
of the beam being defocused to extend backwards to the point where the witness beam wakefields are no longer in the
blow-out regime. At around $3\cdot\sigma_{x,eb}$ emittance is no longer preserved at all.
